---
title: "Mini-Project 2"
author: "Dardalie Brooks and Janell Lin"
date: "March 16,2018"
output: html_document
---


```{r}
library(tidyverse)
library(mosaic)
#library(magrittr)
```


## Loading the data

This project is so interesting and relevant to my life!

```{r, include=FALSE}
#Loads data
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")


#Adds file to enviornment
load(file = "house_elections.rda")
load(file="candidates.rda")
load(file="committees.rda")
load(file="contributions.rda")
```


```{r}
library(tidyverse)

elections_1 <- house_elections %>% 
                  select(fec_id,state,incumbent,candidate_name,party,primary_votes,ge_winner)

names(elections_1)[names(elections_1) == 'state'] <- 'STATE'


contr <- contributions %>% 
                  select(state,name,transaction_amt,cand_id,transaction_type,state)%>% 
                  filter(transaction_type%in%c("24A","24E","24N","24F")) %>% 
                  mutate(Cand_Funding=if_else(transaction_type%in%c("24E","24F"),"FOR","AGAINST"))


names(elections_1)[names(elections_1) == 'fec_id'] <- 'cand_id'

contr_incum <-contr  %>%
  inner_join(elections_1, by = "cand_id")%>% 
    group_by(cand_id,Cand_Funding,candidate_name,party,cand_id,ge_winner,incumbent,STATE) %>%
  summarise(num = n(),
              totalDonation = sum(transaction_amt))%>%
  spread (key=Cand_Funding, value=totalDonation)


```




```{r}
CA<-contr_incum %>%
  filter(STATE== "CA")%>%
  select(candidate_name, cand_id,Cand_Funding,party,cand_id,ge_winner,incumbent,STATE, totalDonation)
  

<<<<<<< HEAD
ggplot(data=CA,aes(x=candidate_name,y=FOR, fill=incumbent,na.rm = FALSE))+
  geom_bar(stat="identity")+
  
=======
ggplot(data=CA,aes(x=candidate_name,y=FOR, fill=incumbent, na.rm = FALSE))+
  geom_bar(stat="identity")
>>>>>>> 92b9aadfbd72510affe086870f85cd9e43a6b321
  
```



```{r}
MA<-contr_incum %>%
  filter(STATE== "MA")%>%
  select(candidate_name,cand_id,party,cand_id,ge_winner,incumbent,STATE,FOR,AGAINST,num)
# looks @ MA data ONLY

<<<<<<< HEAD
ggplot(data=MA,aes(x=candidate_name,y=FOR, fill=incumbent,na.rm=F,ifelse(color==ge_winner,"W","N")))+
  geom_bar(stat="identity")+
  theme_minimal()
##### Money FOR candidate

ggplot(data=MA,aes(x=candidate_name,y=AGAINST, fill=incumbent,na.rm=F,color=ge_winner))+
  geom_bar(stat="identity")+
  theme_minimal()
##### Money AGAINST candidate
=======
ggplot(data=MA,aes(x=candidate_name,y=FOR, fill=incumbent,na.rm=T))+
  geom_bar(stat="identity")

ggplot(data=MA,aes(x=candidate_name,y=AGAINST, fill=incumbent,na.rm=T))+
  geom_bar(stat="identity")
>>>>>>> 92b9aadfbd72510affe086870f85cd9e43a6b321


```



```{r}
types_con <- contributions %>%     
          group_by(transaction_type) %>% 
          summarise(N=n())
#gives amount of unique transaction types

#rapply(contributions,function(x)length(unique(x))) 
```


##### Transaction Type Key:
24A -> Independent expenditure opposing election of candidate  ####AGAINST 
24E -> Independent expenditure advocating election of candidate   #####FOR
24F -> Communication cost for candidate (only for Form 7 filer)   #######FOR
24N -> Communication cost against candidate (only for Form 7 filer)   ####AGAINST 


24C -> Coordinated party expenditure
24K-> Contribution made to nonaffiliated committe
24R -> Election recount disbursement
24Z -> In-kind contribution made to registered filer   #FOR   **non-monetary

