---
title: "Mini-Project 2"
author: "Dardalie Brooks and Janell Lin"
date: "March 16,2018"
output: html_document
---


```{r,fig.width=25,fig.height=11,message=FALSE,warning=FALSE}
library(tidyverse)
library(mosaic)
library(magrittr)
library(RColorBrewer)
library(ggthemes)
extrafont::loadfonts(device="win")
```


## Loading the data

This project is so interesting and relevant to my life!

```{r, include=FALSE}
#Loads data
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")


#Adds file to enviornment
load(file = "house_elections.rda")
load(file="candidates.rda")
load(file="committees.rda")
load(file="contributions.rda")
```


```{r}

elections_1 <- house_elections %>%
  select(fec_id,state,incumbent,candidate_name,party,primary_votes,ge_winner)

names(elections_1)[names(elections_1) == 'state'] <- 'STATE'


contr <- contributions %>% 
                  select(state,name,transaction_amt,cand_id,transaction_type,state)%>% 
                  filter(transaction_type%in%c("24A","24E","24N","24F")) %>% 
                  mutate(Cand_Funding=if_else(transaction_type%in%c("24E","24F"),"FOR","AGAINST"))


names(elections_1)[names(elections_1) == 'fec_id'] <- 'cand_id'

contr_incum <-contr  %>%
  inner_join(elections_1, by = "cand_id")%>% 
    group_by(cand_id,Cand_Funding,candidate_name,party,cand_id,ge_winner,incumbent,STATE) %>%
  summarise(num = n(),
              totalDonation = sum(transaction_amt))%>%
  spread (key=Cand_Funding, value=totalDonation)


```



```{r}
# looks @ MA data ONLY
MA<-contr_incum %>%
  filter(STATE== "MA")%>%
  select(candidate_name,cand_id,party,cand_id,ge_winner,incumbent,STATE,FOR,AGAINST,num)

# looks @ NY data ONLY
NY<-contr_incum %>%
  filter(STATE== "NY")%>%
  select(candidate_name,cand_id,party,cand_id,ge_winner,incumbent,STATE,FOR,AGAINST,num)

##### Money FOR candidate

ggplot(data=MA,aes(x=candidate_name,y=FOR, fill=incumbent,ifelse(color==ge_winner,"W","N")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  theme(axis.text=element_text(size=14,face="bold")) 

#table with for/against for MA
contr_incum_FA_MA <-contr  %>%
  inner_join(elections_1, by = "cand_id")%>% 
    group_by(cand_id,Cand_Funding,candidate_name,party,cand_id,ge_winner,incumbent,STATE) %>%
  summarise(num = n(),
              totalDonation = sum(transaction_amt))%>%
  filter(STATE== "MA")%>%
  mutate()
  select(candidate_name,cand_id,Cand_Funding,party,cand_id,ge_winner,incumbent,STATE,num, totalDonation)


# looks @ MA data, contributions"FOR" ONLY
contr_incum_F <-contr  %>%
  inner_join(elections_1, by = "cand_id")%>% 
    group_by(cand_id,Cand_Funding,candidate_name,party,cand_id,ge_winner,incumbent,STATE) %>%
  summarise(num = n(),
              totalDonation = sum(transaction_amt))%>%
  filter(STATE== "MA", Cand_Funding=="FOR")%>%
  select(candidate_name,cand_id,Cand_Funding,party,cand_id,ge_winner,incumbent,STATE,num, totalDonation)


# looks @ MA data, contributions"AGAINST" ONLY
contr_incum_A <-contr  %>%
  inner_join(elections_1, by = "cand_id")%>% 
    group_by(cand_id,Cand_Funding,candidate_name,party,cand_id,ge_winner,incumbent,STATE) %>%
  summarise(num = n(),
              totalDonation = sum(transaction_amt))%>%
  filter(STATE== "MA", Cand_Funding=="AGAINST")%>%
  select(candidate_name,cand_id,Cand_Funding,party,cand_id,ge_winner,incumbent,STATE,num, totalDonation)

##### Money AGAINST candidate



ggplot(data=contr_incum_FA_MA,aes(x=candidate_name, y = totalDonation))+
  geom_bar(aes( fill=Cand_Funding), stat = "Identity", position="stack")+
  labs(title ="MA Candidates", 
       subtitle="Contributions Against Candidates",
       caption ="FEC")+
  facet_wrap(~as.factor(incumbent), scales = "free_x")+
  scale_y_continuous("Contributions in USD (Million)", 
                     limits = c(0,5000000),
                     breaks=c(0.00,1000000, 2000000,3000000, 4000000, 5000000),
                     labels= c("0","1","2", "3", "4","5"))+                     
  scale_x_discrete("Candidate Name")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        panel.grid.major = element_blank())+
  geom_text(aes(label = contr_incum_FA_MA$totalDonation, hjust = 0),position = position_dodge(width = 0.9))+
  geom_text(aes(label = contr_incum_FA_MA$ge_winner, hjust = 1),position = position_dodge(width = 0.9), color="red")



```




Function for plotting graphs of 50 states
```{r}
incumbent_name <- list(
  'True'="incombuent",
  'FALSE'="NEW")



#table with for/against
contr_incum_FA <-contr  %>%
  inner_join(elections_1, by = "cand_id")%>% 
    group_by(cand_id,Cand_Funding,candidate_name,party,cand_id,ge_winner,incumbent,STATE) %>%
  summarise(num = n(),
              totalDonation = sum(transaction_amt))%>%
  select(candidate_name,cand_id,Cand_Funding,party,cand_id,ge_winner,incumbent,STATE,num, totalDonation)



basic_plot <- function(STATE_arg) {
  contr_incum_FA <- contr_incum_FA%>%
    filter(STATE == STATE_arg)

#Table that have only the lowest donations
low_values<-contr_incum_FA %>%
  filter(totalDonation<20000)  

#Table that only have winnders
winners<-contr_incum_FA %>%
  filter(ge_winner=="W")
    
ggplot(data=contr_incum_FA,aes(x=candidate_name, y = totalDonation))+
  geom_bar(aes( fill=Cand_Funding), stat = "Identity", position="stack")+
  facet_wrap(~as.factor(incumbent), scales = "free_x", labeller = as_labeller(incumbent_name))+
  scale_y_continuous("Contributions in USD (Million)", 
                     limits = c(0,5000000),
                     breaks=c(0.00,1000000, 2000000,3000000, 4000000, 5000000),
                     labels= c("0","1","2", "3", "4","5"))+                     
  scale_x_discrete("Candidate Name")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        panel.grid.major = element_blank())+
  geom_text(data=low_values, aes(label =totalDonation, hjust = 0),position = position_dodge(width = 0.9))+
  geom_text(data=contr_incum_FA, aes(label = ge_winner, hjust = 1),position = position_dodge(width = 0.9), color="red")
}

basic_plot(STATE_arg = "MA")

basic_plot(STATE_arg="NY")

NY<-contr_incum %>%
  filter(STATE== "NY")%>%
  select(candidate_name,cand_id,party,cand_id,ge_winner,incumbent,STATE,FOR,AGAINST,num)



```






```{r}
types_con <- contributions %>%     
          group_by(transaction_type) %>% 
          summarise(N=n())
#gives amount of unique transaction types

#rapply(contributions,function(x)length(unique(x))) 
```

#One method to change name color
a <- ifelse(contr_incum$ge_winner=="W", "blue", "red")


##### Transaction Type Key:
24A -> Independent expenditure opposing election of candidate  ####AGAINST 
24E -> Independent expenditure advocating election of candidate   #####FOR
24F -> Communication cost for candidate (only for Form 7 filer)   #######FOR
24N -> Communication cost against candidate (only for Form 7 filer)   ####AGAINST 


24C -> Coordinated party expenditure
24K-> Contribution made to nonaffiliated committe
24R -> Election recount disbursement
24Z -> In-kind contribution made to registered filer   #FOR   **non-monetary


