---
title: "Mini-Project 2"
author: "Dardalie Brooks and Janell Lin"
date: "March 16,2018"
output: html_document
---


```{r,fig.width=25,fig.height=11,message=FALSE,warning=FALSE}
library(tidyverse)
library(mosaic)
library(magrittr)
library(RColorBrewer)
library(ggthemes)
library(scales)
```


## Loading the data

This project is so interesting and relevant to my life!

```{r, include=FALSE}
#Loads data
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")

```


```{r}

elections_1 <- house_elections %>%
  select(fec_id,state,incumbent,candidate_name,party,primary_votes,ge_winner) %>% 
  mutate(ge_winner =ifelse(ge_winner=="W", "W","")) %>% 
   mutate(incumbent =ifelse(incumbent=="TRUE", "INCUMBENT","NEW CANDIDATE"))

names(elections_1)[names(elections_1) == 'state'] <- 'STATE'


contr <- contributions %>% 
                  select(state,name,transaction_amt,cand_id,transaction_type,state)%>% 
                  filter(transaction_type%in%c("24A","24E","24N","24F")) %>% 
                  mutate(Cand_Funding=if_else(transaction_type%in%c("24E","24F"),"FOR","AGAINST"))


names(elections_1)[names(elections_1) == 'fec_id'] <- 'cand_id'

contr_incum <-contr  %>%
  inner_join(elections_1, by = "cand_id")%>% 
    group_by(cand_id,Cand_Funding,candidate_name,party,cand_id,ge_winner,incumbent,STATE) %>%
  summarise(num = n(),
              totalDonation = sum(transaction_amt))%>%
  spread (key=Cand_Funding, value=totalDonation)


```



```{r}
# looks @ MA data ONLY
MA<-contr_incum %>%
  filter(STATE== "MA")%>%
  select(candidate_name,cand_id,party,cand_id,ge_winner,incumbent,STATE,FOR,AGAINST,num)


#table with for/against for MA
contr_incum_FA_MA <-contr  %>%
  inner_join(elections_1, by = "cand_id")%>% 
    group_by(cand_id,Cand_Funding,candidate_name,party,cand_id,ge_winner,incumbent,STATE) %>%
  summarise(num = n(),
              totalDonation = sum(transaction_amt))%>%
  filter(STATE== "MA")%>%
  mutate()
  select(candidate_name,cand_id,Cand_Funding,party,cand_id,ge_winner,incumbent,STATE,num, totalDonation)



##### Convert incumbent to factor
contr_incum_FA$incumbent <- as.factor(contr_incum_FA$incumbent)

#####

ggplot(data=contr_incum_FA,aes(x=candidate_name ))+
  geom_bar(aes( y = totalDonation,fill=Cand_Funding), stat = "Identity", position="stack")+
  labs(title ="MA Candidates", 
       caption ="FEC")+
  facet_wrap(~as.factor(incumbent),scales="free_x")+
  scale_y_continuous("Contributions in USD (Million)", 
                     limits = c(0,6000000),
                     breaks=c(0.00,1000000, 2000000,3000000, 4000000, 5000000,6000000),
                     labels= c("0","1","2", "3", "4","5","6"))+                     


# looks @ MA data, contributions"AGAINST" ONLY
contr_incum_A <-contr  %>%
  inner_join(elections_1, by = "cand_id")%>% 
    group_by(cand_id,Cand_Funding,candidate_name,party,cand_id,ge_winner,incumbent,STATE) %>%
  summarise(num = n(),
              totalDonation = sum(transaction_amt))%>%
  filter(STATE== "MA", Cand_Funding=="AGAINST")%>%
  select(candidate_name,cand_id,Cand_Funding,party,cand_id,ge_winner,incumbent,STATE,num, totalDonation)


```




DF for plotting graphs of 50 states
```{r}
#table with for/against
contr_incum_FA <-contr  %>%
  inner_join(elections_1, by = "cand_id")%>% 
    group_by(cand_id,Cand_Funding,candidate_name,party,cand_id,ge_winner,incumbent,STATE) %>%
  summarise(num = n(),
              totalDonation = sum(transaction_amt))%>%
  select(candidate_name,cand_id,Cand_Funding,party,cand_id,ge_winner,incumbent,STATE,num, totalDonation)

```



Function for plotting graphs of 50 states

```{r}
basic_plot <- function(STATE_arg) {
  contr_incum_FA <- contr_incum_FA%>%
    filter(STATE == STATE_arg)

#Table that have only the lowest donations
  
low_values<-contr_incum_FA %>%
  filter(totalDonation<20000)

winners<-contr_incum_FA %>%
  filter(ge_winner=="W")

plot<- ggplot(data=contr_incum_FA,aes(x=candidate_name, y = totalDonation))+
  geom_bar(aes( fill=Cand_Funding), stat = "Identity", position="stack")+
  ggtitle("Candidate Funding")+
  scale_x_discrete("Candidate Name",
                   expand = c(0,0))+
  scale_fill_manual(name="Funding Type", values=c("#814812", "#80e5ff"))+
  facet_wrap(~as.factor(incumbent), scales = "free_x",nrow=2)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        panel.grid.minor = element_blank(),
        strip.background=element_rect(fill="beige"))+
  scale_y_continuous("Contributions in USD", 
                     expand = c(0, 0),
                     limits = c(0,6000000),
                     breaks=c(0.00,1000000, 2000000,3000000, 4000000, 5000000,6000000),
                     labels= c("0","1000000","2000000", "3000000", "4000000","5000000","6000000"))+
    geom_text(data=low_values, aes(label =totalDonation, hjust = 0, color = Cand_Funding), angle=90,position = position_dodge(width = 0.9))+
  geom_text(data=contr_incum_FA, aes(label = ge_winner, vjust = -5),position = position_dodge(width = 0.9), color="red",size=4)+
  labs(caption = "H. Wickham. ggplot2: Elegant Graphics for Data Analysis Springer-Verlag New York, 2009.")
}

#plot+geom_point(aes( fill=Cand_Funding), stat = "Identity", position="stack")
  


basic_plot(STATE_arg = "NY")
```


WORD COUNT
###### to get word count output, run following






![`Github Repository`](https://github.com/Dardalie/sds192-mp2-1) 

```{r}
#wordcountaddin:::text_stats_fn_(text)
```



```
 scale_x_discrete("Candidate Name")+
  scale_y_continuous("Contributions in USD", 
                    limits = c(0,5000000),
                     breaks=c(0.00,1000000, 2000000,3000000, 4000000, 5000000),
                     labels= c("0","1000000","2000000", "3000000","4000000","5000000"))+
  scale_fill_manual("FUnding Purpose", values=c("#814812","#2A8DBC"))+




 #If you want the heights of the bars to represent values in the data, use stat="identity" and map a value to the y aesthetic

```






```{r}
types_con <- contributions %>%     
          group_by(transaction_type) %>% 
          summarise(N=n())

#gives amount of unique transaction types

#rapply(contributions,function(x)length(unique(x))) 
```

#One method to change name color
a <- ifelse(contr_incum$ge_winner=="W", "blue", "red")


##### Transaction Type Key:
24A -> Independent expenditure opposing election of candidate  ####AGAINST 
24E -> Independent expenditure advocating election of candidate   #####FOR
24F -> Communication cost for candidate (only for Form 7 filer)   #######FOR
24N -> Communication cost against candidate (only for Form 7 filer)   ####AGAINST 


24C -> Coordinated party expenditure
24K-> Contribution made to nonaffiliated committe
24R -> Election recount disbursement
24Z -> In-kind contribution made to registered filer   #FOR   **non-monetary



